### 2020-10-31 Thesis-Chapter2-Background.tex
Write contributing factors map section

\paragraph*{\Ac{horsemen}} In the 1990s, an influential encryption advocate coined the phrase ``\ac{horsemen-full}'' to
describe four reasons that governments and law enforcement agencies use to undercut public support for strong encryption
\cite{may_1994}. The traditional list includes terrorists, pedophiles, drug dealers, and money launderers, though
sometimes kidnappers are substituted for money launderers \cite{schneier_scaring_2019}. Reflecting the times,
\ac{the-cw1} emphasized drug trafficking whereas \ac{the-cw2} is emphasizing terrorism and child pornography
\cite{schulze_clipper_2017}. The focus on terrorism is likely a result of culture that emerged from the September 11
terror attacks as well as the San Bernardino terror attack that launched the Apple vs. \ac{FBI} case; the focus on child
pornography is likely a result of the growth of the ``dark web'' and a revelatory 2019 investigation by the \textit{New
York Times} \cite{keller_internet_2019}.

>>>>

\paragraph*{The \Ac{horsemen}} In the 1990s, an influential encryption advocate coined the phrase ``\ac{horsemen-full}'' to
describe four reasons that governments and law enforcement agencies use to undercut public support for strong encryption
\cite{may_1994}. The traditional list includes terrorists, pedophiles, drug dealers, and money launderers, though
sometimes kidnappers are substituted for money launderers \cite{schneier_scaring_2019}. Reflecting the times,
\ac{the-cw1} emphasized drug trafficking whereas \ac{the-cw2} is emphasizing terrorism and child pornography (\ac{CSAM})
\cite{schulze_clipper_2017}. The focus on terrorism is likely a result of culture that emerged from the September 11
terror attacks as well as the San Bernardino terror attack that launched the Apple vs. \ac{FBI} case; the focus on
\ac{CSAM} is likely a result of the growth of the ``dark web'' and a revelatory 2019 investigation by the \textit{New
York Times} \cite{keller_internet_2019}.

### 2020-10-31 Thesis-Chapter4-Arguments.tex
Termify argument maps and remove strategy notes
Begin arguments chapter
Write contributing factors map section

% Already covered defining the problem. Next will discuss goals and list alternatives. That will feed into threat
% modeling

\section{Mapping the EA Debate}

\subsection{Desireable Outcomes}

@@

\subsection{Proposed Alternatives}

>>>>

In this chapter we will analyze the \ac{encryption} debate using \acp{argmap}. The maps help one digest the debate, but
there are two important shortcomings of the ones presented here. First, argument mapping is ideally just one tool in the
collaborative process that progressively approaches the problem definition and solution. One can make an approximation
from research, but it is not a replacement for debate arising from live discussion. Second, \acp{argmap} as portrayed in
this thesis can be deceiving about the strength of an argument. Argument nodes show no indication of their strength or
validity; one can formulate ten poor arguments against a single strong one, and a glance at the map will indicate that
the case of the ten is stronger. With those qualifications in mind, let us begin by looking at the factors at the heart
of the conflict.

\section{Contributing Factors}

As previously stated, it is \ac{encryption}'s dual role as enabler of radical privacy and cornerstone of security is at
the heart of the EA debate. Of course, there is only a conflict if one sees radical privacy as a bad thing. The right to
privacy is both a strongly held value and an enshrined legal principle, and many use privacy-based arguments to show
\ac{EA} as socially undesirable. The \ac{snowden} revelations \cite{landau_making_2013} only unveiled the scale of
privacy-eroding U.S. government surveillance enabled by technological changes, terrorism-motivated policies, and weak
oversight \cite{shamsi_2011}. Violations of privacy are concerning for those most vulnerable and for society at large.
For example, Saudi journalist Jamal Khashoggi's private communications were surveilled by the Saudi government before he
became a victim of politically motivated murder \cite{liebermann_2019}. At a societal level, presence of surveillance
alone changes behavior and chills free speech \cite{rogaway_moral_2015}, while government violations of the law degrade
institutional trust.

The government, and particularly \acl{LE}, argues that encryption is handcuffing their investigational capacity. The
\ac{FBI} has branded strong encryption as ``warrant-proof'' and states that ``the government often cannot obtain the
electronic evidence necessary to investigate and prosecute threats to public and national safety'' \cite{fbi_2020}. The
pro-\ac{EA} argument is typically rooted in public safety: investigators need access to evidence to fulfill their
commission to catch and convict lawbreakers, and encryption is making that too difficult. Five-eyes nations regularly
put out joint statements expressing their frustration with encryption \cite{ministerial_2018} \cite{goodale_2017}, and
were joined in 2020 by India and Japan in a statement emphasizing the growing danger of \ac{CSAM} \cite{intl_2020}.
Child pornography is one the original \ac{horsemen} that some argue are used to scare people into supporting backdoors
\cite{schneier_scaring_2019}, but it is also a problem growing to astonishing proportions. The \textit{New York Times}'s
2019 investigation on the matter quoted one law enforcement officer as estimating that 400,000 New Jerseyans, more than
4\% of the state's population, could be charged with violating child exploitation material laws
\cite{keller_internet_2019}.

Unfortunately, shocking assertions such as this have not been independently confirmed or backed up with hard data.
Intelligence agencies have a long history or misrepresenting positions and overstepping bounds
\cite{johnson_congressional_2004} \cite{shamsi_2011}, and this has led to lack of institutional trust undercutting their
claims that they need \ac{EA}. Indeed, the \ac{FBI} has already been caught exaggerating by several times how many
mobile devices they could not access due to \acl{DE} \cite{devlin_2018}. As Rozenshtein says on this subject, ``It is
impossible to know the precise extent to which encryption frustrates law-enforcement investigations, both because
law-enforcement agencies are only beginning to collect accurate statistics, and because one can never be sure of how an
investigation would have proceeded in the absence of encryption'' \cite{rozenshtein_wicked_2018}, but it is still
crucial to have an accurate depiction of the problem in order to come to justified and helpful solutions. This argument
is analyzed further in the next section.

Information security is a the remaining central issue in the debate. As described in \mysec{sec-crypto-basics},
\ac{cryptography} in various forms plays a foundational technical role in nearly every aspect of security, and
information confidentiality itself is one of the primary properties security practitioners fight to protect. Efforts in
the past have sought to undermine the cryptographic foundations of encryption, though this is not a feature of proposals
today, as that is universally seen as too risky. \mysec{sec-tech-approaches} introduced several alternative technical
approaches to \ac{EA}, but experts still proclaim loud and clear that the current state of the art is far from capable
of providing the type of access \acl{LE} in an acceptably secure manner \cite{abelson_2015} \cite{abelson_risks_1997}.
Security was an afterthought in early computing and networking designs, and the field of cybersecurity is still more of
an art the a science; hobbling systems with a mandate to provide \ac{EA} would inevitably diminish security to some
degree \cite{abelson_2015}.

Finally, one may argue that \ac{EA}, depending on its implementation, could have positive auxiliary use cases. It could
enable malware scanning, administrator access in a business setting, or password recovery. Typically these use cases
have other solutions, however, and to combine the requirements of these uses with those of any reasonable \ac{EA}
proposal would likely fatally weaken it.

See \myfig{fig-args-contrib} for the \ac{argmap} representing this section.

\begin{sidewaysfigure}
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.contrib.pdf}
  \caption[Contributing Factors to the EA Debate]{Contributing Factors to the EA Debate}
  \label{fig-args-contrib}
\end{sidewaysfigure}

\section{Going Dark vs. The Golden Age}

% Actually fund initiatives to tackle these problems!
% pfefferkorn_2019
% keller_internet_2019

\section{Eliminating Fallacious Arguments}

\section{EA and Alternatives}

\section{Zooming in on EA}

% - Avoid pitfalls of
%   - Easy answers
%     - EA mandates, complexity denial
%   - Fallacies!
%   - Bad results with long technical tails

% Note: a problem with muddling through wicked problems is that each attempted fix leads to long lasting unintended side
% effects. This is especially true with matters of encryption, where the data could be stored for years till it can be
% decrypted! So must be very careful to avoid solution attempts that leave long scars.

@@

\section{Specific Proposals}
